\chapter{How to read this book?}

\section{Intended audience}
The primary aim of this book is to capture the wealth of output of the first phase of the project and serve as a compendium for teams and individuals participating in bringing Swarm to life in the forthcoming stages.

The book is intended for an audience of more technically inclined readers that are interested in using Swarm in their development stack and wish to go deeper understanding the motivation or design decisions behind the technology. Researchers, academics and decentralisation experts are invited to check our reasoning and audit the sanity of our design. Core developers or developers from the eco-system that build components, tooling or entire client implementations benefit from the specifications as well as the explanations.

\section{Structure of the book}

The book has three major parts. The first (Prelude) (\ref{part:preface}), explains the motivation and history of the Swarm project, the vision and the evolution of technologies needed to achieve the goals.

The second (Design and Architecture), (\ref{part:designarchitecture}), contains a detailed exposition of the design and architecture of Swarm. This part aspires to cover all areas relevant to the core functionality of Swarm.

The third part (Specifications), (\ref{part:specifications}), provides the formal specification of components, which is claimed to be sound and complete to serve as the handbook for Swarm client developers.

The book is complete with index, glossary of terms and acronyms, and an appendix containing formalised arguments.

\section{How to use the book}

The remaining chapters of the Prelude together with the Design and Architecture part can be read as one continuous narrative. Those wishing to just jump right into the technology can start with the Design and Architecture part skipping the prelude.

A Swarm client developer can start from any particular component spec and work one's way back to Design and Architecture via the in-text references if wider context is needed or one is interested in the justification of some of the choices apparent in the specs.

\chapter{About the project}\label{sec:about}
\section{History}
\section{Organisation}
\section{Community}
\section{Ecosystem}
