\newcommand{\person}[1]{{\scshape #1}}
\chapter{Acknowledgments \statusgreen}

\section*{Editing}

Many have helped me write this book, but a few that took very active roles in making it happen are due credit. \person{Daniel Nickless} is the man behind all the diagrams; we enjoyed many hours of my giving birth to impromptu visualisations, and he was happy to redo them several times. Dan is a virtuoso of Illustrator and has also become a LaTeX expert to typeset some nice trees. 

I am hugely indebted to \person{Črt Ahlin} who, beside managing the book project, has contributed some top-quality text.
He also undertook many of the unrewarding, tedious jobs of compiling the indexes and glossaries. Both Črt and Dan (a native speaker of English), as well as \person{Attila Lendvai}, did an amazing job at proofreading and correcting mistakes and typos.
The second edition has seen a major upgrade in text quality due to the arduous work of \person{Andrea Robert}.

Special thanks are due to \person{Edina Lovas}, whose support and enthusiasm have always helped push me along. 

\section*{Authors}

Swarm is co-fathered by my revered friend and colleague, the awesome \person{Daniel A. Nagy}.  Daniel invented the fundamental design of Swarm and should get the credit for quite a few major architectural decisions, innovative ideas, and formal insights presented in this book. 

\person{Aron Fisher}'s contribution to Swarm would be hard to overstate. Most of what Swarm is now started or got worked out in sessions with Aron.  He not only contributed ingredients overall, but also co-authored the first few orange papers and, not least, was always at the forefront, presenting and explaining our tech in conferences and meetups.

I thank Daniel and Aron for bearing with me, enduring my sloppy, half-baked ideas, bringing clarity, and always understanding the maths.
Without claiming full endorsement or any responsibility for what is written here,
I would consider Daniel and Aron as co-authors of this book.

I owe deep gratitude to my partner in crime, \person{Gregor Žavcer}, who has been running the project, currently serving as director of the Swarm Foundation. Gregor's honest fascination and unrelenting dedication to the project kept me going through many a low moment in the past. Our shared vision of a decentralised future data economy, ranging from technological innovation to ethical direction, served as the foundation for our collaboration. A substantial portion of this book has been shaped during our night-long brainstorming sessions. Gregor even contributed content to the book.

I would like to thank \person{Rinke Hendriksen} and \person{Ábel Bodó}, who contributed significant insight and innovation, mainly in the area of incentivisation. 
Further major contributions to both underlying concepts and their presentation came from \person{Fabio Barone}, \person{Ralph Pilcher} on incentives,  
\person{Javier Peletier} on feeds, and \person{Louis Holbrook} on feeds and pss. Last but not least, our resident genius \person{Viktor Toth}, aka \person{Nugaon},
continues to amaze me with his creativity and ambition.

\section*{Feedback}

The book benefited immensely from feedback. Those who went through the pain of reading early versions and provided comments on the work in progress, offering their criticism or pointing out areas of unclarity, deserve to be mentioned: \person{Henning Dietrich}, \person{Brendan Graetz}, \person{Attila Lendvai},  people from IOV labs:  \person{Marcelo Ortelli}, \person{Santiago Regusci}, \person{Vojtěch Šimetka};
and people from the Swarm team:
\person{Ábel Bodó}, 
\person{Elad Nachmias}, \person{Janoš Guljaš},  \person{Petar Radović}, \person{Louis Holbrook}, and \person{Zahoor Mohamed}.



\section*{Conception and influences}

The book of Swarm is itself an expression of the grand idea behind Swarm: [the pursuit of] the vision of a decentralised storage and messaging system built on top of the blockchain. The concept and initial formulation of Swarm as one of the pillars of a holy trinity to realise the Decentralised Web appeared before the launch of Ethereum in early 2015. It was by Ethereum founders \person{Vitalik Buterin}, \person{Gavin Wood}, and \person{Jeffrey Wilcke} that Swarm was trolled onto the slippery slope of bee jokes and geek humor. The protocol tags \emph{bzz} and \emph{shh} were both coined by Vitalik. 

People who were close to the cradle of Swarm include \person{Alex Leverington} and \person{Felix Lange}. Early discussions with them catalysed fundamental decisions that led to the design of Swarm as it now presents.

The foundations of Swarm were laid over the course of 2015.
Daniel worked with \person{Zsolt Felföldi}, of light client fame, whose code is still being seen here and there in the Go Ethereum-based Swarm implementation. His ideas clearly have a hallmark on what Swarm set out to be. 

We are hugely indebted to \person{Elad Verbin}, who for years has been acting as a scientific as well as strategic advisor to Swarm. Elad put considerable effort into the project, and his unparalleled insight and depth of understanding across all aspects of Swarm have been invaluable. Particularly, his understanding of the isomorphism between pointer-based functional data structures and content-addressed distributed data had a major impact on how we handle higher-level functionality. Our work on a swarm interpreter inspired the Swarm script.

Special thanks are due to \person{Daniel Varga}, \person{Attila Lendvai}, and \person{Attila Gazsó} for the long nights of brainstorming, I have learnt an awful lot from each of you. Thanks to \person{Alexey Akhunov} and \person{Jordi Baylina} for major technical insights and inspiration.
My very special friend, \person{Anand Jaisingh}, deserves my gratitude for his unshakeable trust in me and the project, and for the unique inspiration and synergy catalysed by his presence in the halo of Swarm.

Early in the project, we spent quite some time with \person{Alex van der Sande} and \person{Fabian Vogelsteller}, engaging in discussions about Swarm and its potentials. Many ideas that came to life as a result, including manifests and the HTTP API, owe them credit. People in or around the Ethereum Foundation who shaped the idea of Swarm include \person{Taylor Gerring}, \person{Christian Reitwiessner}, \person{Stephan Tual}, \person{Alex Beregszaszi}, \person{Piper Merriam}, and \person{Nick Savers}. 

\section*{Team}

First and foremost, thanks to \person{Jeffrey Wilcke}, one of the three founders and team lead of the Amsterdam go-ethereum team. He was supporting the Ethersphere subteam Dani, Fefe, and me, protecting the project in times of austerity.
I am forever grateful to all current and past members of the Swarm team: ethernal gratitude to \person{Nick Johnson}, who, during the brief period he was on the team, created ENS. I extend my gratitude to those special individuals who have been with the team for the longest time: \person{Louis Holbrook}, \person{Zahoor Mohamed}, and \person{Fabio Barone}. Their creativity and faith have been instrumental in helping us navigate through rough  times. Thanks to \person{Anton Evangelatov}, \person{Bálint Gábor}, \person{Janoš Guljaš}, and \person{Elad Nachmias} for their massive contributions to the codebase. Thanks to \person{Ferenc Szabó}, \person{Vlad Gluhovsky}, \person{Rafael Matias}, and many others that cannot be named but hae contributed to the code.
\person{Ralph Pichler} deserves a special mention as he has been a keen follower and supporter of our project for many years. Gradually, he became an honorary member of the team, and played a pivotal role in implementing the initial version of the entire smart contract suite for swap, swear, and swindle. Additionally, he drove the development of blockchain interaction, bandwidth incentives, and key management.

Major kudos to \person{Janoš Guljaš}, who bravely took over the role of engineering lead and created a new killer team in Belgrade with the excellent \person{Petar Radović}, \person{Svetomir Smiljković}, and \person{Ivan Vandot}.  

I am grateful to \person{Vojtěch Šimetka} and the Swarm contingent at IOV labs, who played a crucial role in saving the project. \person{Marcelo Ortelli and Santiago Regusci} have been major contributors to the current codebase, alongside the Belgrade team. 

I would also like to thank \person{Tim Bansemer}, who is one of a kind, with unimaginable effectiveness and drive. His contributions will always be felt in and around the team, the code, the documentation, and the processes.

The latest `bee` codebase is mainly the work of the \emph{four musketeers}: \person{Alok Nerurkar}, \person{Esad Akar}, \person{Anatol Lupanescu}, and \person{Peter Mrekaj}, recruited by the legendary and elusive \person{Elad Nachmias}. This core team received assistance from \person{Vlado Pajić} and \person{Marko Blazević}.



Special big thanks to the irreplaceable \person{Gyuri Barabás}, our resident stats and maths guru, whose contributions are of immense importance. Swarm would not have been anywhere without the legend \person{Callum Toner}, who pulled together all R\&D efforts and led the project to deliver an actually working product virtually single-handedly.



\section*{Ecosystem}

Swarm has always attracted a wide community of enthusiasts as well as an ecosystem of companies and projects whose support and encouragement kept us alive during some dark days. 
Special thanks goes to \person{Jarrad Hope}, \person{Jacek Sieka}, and \person{Oscar Thoren} of Status, \person{Marcin Rabenda} of Consensys, \person{Tadej Fius}, \person{Zenel Batagelj} from Datafund, \person{Javier and Alfonso Peletier} of Epic Labs, \person{Eric Tang} and \person{Doug Petkanics} of LivePeer, \person{Sourabh Niyogi} of Wolk, \person{Lewis Marshall}, \person{Vaughn McKenzie}, \person{Fred Tibbles} and \person{Oren Sokolovsky} of JAAK, \person{Carl Youngblood}, \person{Paul Le Cam}, \person{Shane Howley}, and \person{Doug Leonard} from Mainframe. We are also grateful for the contributions of \person{Anand Jaisingh}, \person{Dimitry Kholkhov}, \person{Igor Sharudin} of BeeFree, and \person{Attila Gazsó} from the Felfele Foundation. 

Recently, we have received massive amounts of help from two unaffiliated community members, known by their Discord handles as \person{ldeffenb} and \person{mfw78}.

I would like to thank all participants of Swarm Summits, hack weeks, and other gatherings. Many of the ideas in this book were born from the conversations held during these events. I also want to thank \person{Michelle Thuy} and \person{Kevin Mohanan}.

Finally, my deepest gratitude goes to my mentors and teachers, \person{András Kornai}, \person{László Kálmán}, \person{Péter Halácsy}, and \person{Péter Rebrus}, who have shaped my thinking and skills. They will always be my intellectual heroes.

