\subsection{Overlay address \statusyellow}

Swarm's overlay network uses 32-byte addresses. In order to help  uniform utilisation of the address space,  these addresses must be derived using a hash function. A Swarm node must be associated a \gloss{Swarm base account} or \gloss{bzz account}, which is an Ethereum account that the node (operator) must possess the private key for. The node's overlay address is derived the public key of this account. 

\begin{definition}[Swarm overlay address of node A]\label{def:overlay}
\begin{equation}
\mathit{overlayAddress}(A) \defeq \mathit{Hash}(\mathit{ethAddress}|\mathit{bzzNetworkID})         
\end{equation}
where
\begin{itemize}
\item $\mathit{Hash}$ is the 256-bit Keccak SHA3 hash function
\item \emph{ethAddress} - the ethereum address  (bytes,  not hex) derived from the node's base account public key: $\mathit{account}\defeq\mathit{PubKey}(K_A^\mathit{bzz})[12:32]$), where
    \begin{itemize}
    \item \emph{PubKey} is the \emph{uncompressed} form of the public key of a keypair \emph{including} its $04$ (uncompressed) prefix.
    \item $K_A^\mathit{bzz}$ refers to the node's bzz account key pair
    \end{itemize}
\item \emph{bzzNetworkID} is the bzz network id of the swarm network serialised as a little-endian binary \emph{uint64}.
\end{itemize}
\end{definition}

In a way, deriving the node address from a public key means the overlay address space is not freely available: to occupy an address you must possess the private key of the address which other nodes need to verify. Such authentication is easy using a digital signature of a shared consensual piece of text, see \ref{spec:format:bzzaddress}.

\subsection{Underlay address \statusyellow}

To enable peers to locate the a node on the network, the overlay address is paired with an underlay address. The underlay address is a string representation of the node's network location on the underlying transport layer. It is used by nodes to dial other nodes to establish keep-alive peer to peer connections. 

\begin{definition}[Swarm underlay multiaddress]\label{def:underlay}
\begin{lstlisting}[]

\end{lstlisting}
\end{definition}


\subsection{BZZ address \statusyellow}

Bzz address is functionally the pairing of overlay and underlay addresses. In order to ensure that an overlay address is derived from an account the node possesses as well as verifiably attest to an underlay address a node can be called on, bzz addresses are communicated in the following transfer format:

\begin{definition}[Swarm bzz address transfer format]\label{def:bzz-address}
\begin{lstlisting}[]
// ID: /swarm/handshake/1.0.0/bzzaddress

syntax = "proto3";

message BzzAddress {
    bytes Underlay = 1;
    Signature Sig  = 2;
    bytes Overlay  = 3; 
}
\end{lstlisting}
\end{definition}

Here the signature is attesting to the association of an overlay and an underlay address for a network. 

\begin{definition}[Signed underlay address of node A]\label{def:signed-underlay}
\begin{equation}
\mathit{signedUnderlay}(A) \defeq \mathit{Sign}(\mathit{underlay}|\mathit{bzzNetworkID})         
\end{equation}
\end{definition}

of the underlay with bzz network ID appended as plaintext and hashes the resulting public key together with the bzz network ID. 

\begin{definition}[Node addresses: overlay, underlay,  bzz address]\label{def:bzz-types}
\begin{lstlisting}[language=buzz1]
// /bzz

define type overlay as [segment size]byte
define type underlay []byte

define function overlay.address of pubkey 
    within @network uint64 
as
    hash @pubkey address and @network 
        as overlay

define function valid bzz.address 
    within @network uint64
as
    assert @bzz.address overlay == overlay.address of crypto/recover from @bzz.address signature with @bzz.address @underlay
        within @network
        
define function bzz.address of overlay
    from underlay 
    by @account ethereum/address
as
    @sig = crypto/sign @underlay by @account
    bzz.address{ @overlay, @underlay, @sig }

\end{lstlisting}
\end{definition}




In order to get the overlay address from the transfer format peer info, one recovers from signature the peer's base account public key using the plaintext that is constructed as per \ref{def:signed-underlay}. From the public key, the overlay can be calculated as in \ref{def:overlay}. The overlay address thus obtained needs to be checked against the one provided in the handshake.

Signing of the underlay enables preflight authentication of the underlay of a trusted but not connected node. 

Since underlays are meant to be volatile, we can assume and in fact expect multiple underlays signed by the same node. However, these are meant to be temporally ordered. So one with a newer timestamp invalidates the older one. 

In order to make sure that the node connected through that underlay does indeed operate the overlay address, its authentication must be obtained through the peer connection that was initiated by dialing the underlay. The This protects against malicious impersonation of a trusted overlay potentially. 